Numerical simulation of the Cordilleran ice sheet through the last glacial cycle

### 2014-05-27 cordillera-cycle.tex
Small corrections regarding snapshots.

% fig:snapshots
\begin{figure}
  \includegraphics{snapshots}
  \caption{Snapshots of modelled ice surface topography (1\,\unit{km} contours)
           and velocity (\unit{m\,yr^{-1}}) at modelled times of glacial
           extrema, corresponding to MIS~4, 3, and 2.}
  \label{fig:snapshots}
\end{figure}

>>>>

% fig:snapshots
\begin{figure}
  \includegraphics{snapshots}
  \caption{Snapshots of modelled ice surface topography (500\,\unit{m}
           contours) at modelled times of glacial
           extrema, corresponding to MIS~4, 3, and 2.}
  \label{fig:snapshots}
\end{figure}
